On the number of tiles visited by a\\ line segment on a rectangular grid

### 2021-09-02 paper.tex
Typos
Typo
New figure for proof of proposition on the minimal sufficient set

\begin{figure}
\centering%
\includegraphics[width=.85\textwidth]{examples_1p35}%
\caption{Examples for $a=1.35, b=1$; $\len=1$, $\len=2.4$ and $\len=4.7$
}%
\label{fig: examples}%
\end{figure}%

@@

\begin{proof}
***New proof based on treating i,j as continuous along the line i+j=constant, then quantizing to the nearest allowed point along that line. We should the notation $\isolr$, $\jsolr$ for the continuous coordinates, in conformity to other proofs that use continuous coordinates.
% ***The continuous argument gives something like $i-2 = b^2/(a^2+b^2)*(t-3)$, $j = a^2/(a^2+b^2)*(t-3)$. We then compute how much the distance from $(i,j)$ to $(2,2)$ is increased by quantizing along the i+j line, to argue that the nearest quantized point should be chosen. To ensue that in case of a tie we choose the point with larger $i$, we apply floor(...+1/2) to i and ceiling(...-1/2) to j.

@@

%\begin{figure}%
%\centering%
%\includegraphics[width=.7\textwidth]{ijLS_1p35_detail_inverse}%
%\caption{***Figure illustrating the proof of Proposition~\ref{prop: min suff set, form}. Example with $a=1.35, b=1$%
%}%
%\label{fig: ***}%
%\end{figure}%
\end{proof}

@@

The two possibilities are illustrated in Figure~\ref{fig: ijLS_1p35_detail} for $a=1.35, b=1$. In each case, the arc displayed in the graph is centered at $(2a,2b)$ and has radius $\len$. The inner region defined by the arc contains all $(i,j)$ pairs that are achievable according to Proposition~\ref{prop: len ineq i j}.\ref{prop: len ineq i j: ineq, exist}. As in previous figures, filled circles represent $(i,j)$ pairs that are in $\mss$, and empty circles are those that do not belong to $\mss$. The solid line is \eqref{eq: lower bound, line}. The intersection point $(\isolr, \jsolr)$ is displayed with a square marker.

\begin{figure}
\centering%
\subfigure[$\len = 3.1$: $(\isoli,\jsoli) \in \mss$]{%
\label{fig: ijLS_1p35_detail_in}%
\includegraphics[width=.7\textwidth]{ijLS_1p35_detail_in}%
}\\%\hfill%
\subfigure[$\len = 3.7$: $(\isoli,\jsoli) \notin \mss$]{%
\label{fig: ijLS_1p35_detail_notin}%
\includegraphics[width=.7\textwidth]{ijLS_1p35_detail_notin}%
}%
\caption{Obtaining $(\isoli,\jsoli)$ in Theorem~\ref{theo: funt, form}. Examples with $a=1.35, b=1$%
}%
\label{fig: ijLS_1p35_detail}%
\end{figure}%

>>>>

\begin{figure}
\centering%
\includegraphics[width=.85\textwidth]{examples_1p35}%
\caption{Examples for $a=1.35$, $b=1$; $\len=1$, $\len=2.4$ and $\len=4.7$
}%
\label{fig: examples}%
\end{figure}%

@@

\begin{proof}
***New proof based on treating i,j as continuous along the line i+j=constant, then quantizing to the nearest allowed point along that line. We should use the notation $\isolr$, $\jsolr$ for the continuous coordinates, in conformity to other proofs that use continuous coordinates.
% ***The continuous argument gives something like $i-2 = b^2/(a^2+b^2)*(t-3)$, $j-2 = a^2/(a^2+b^2)*(t-3)$. We then compute how much the distance from $(i,j)$ to $(2,2)$ is increased by quantizing along the i+j line, to argue that the nearest quantized point should be chosen. To ensure that in case of a tie we choose the point with larger $i$, we apply floor(...+1/2) to i and ceiling(...-1/2) to j.
% ***Reference the figure in the text. The figure is an example with $a=1.35$, $b=1$, $\tiles=7$. It contains the line j-2 = a^2/b^2*(i-2), whose intersection with i+j-1=t (which is perpendicular to it) gives the continuous solution $(\isolr, \jsolr)$ (marked with a square).

@@

\begin{figure}%
\centering%
\includegraphics[width=.7\textwidth]{mss}%
\caption{Obtaining $(\isolr, \jsolr)$ and $(i_\tiles, j_\tiles)$ in  Proposition~\ref{prop: min suff set, form}. Example with $a=1.35$, $b=1$, $\tiles=7$%
}%
\label{fig: min suff set, form}%
\end{figure}%
\end{proof}

@@

The two possibilities are illustrated in Figure~\ref{fig: ijLS_1p35_detail} for $a=1.35$, $b=1$. In each case, the arc displayed in the graph is centered at $(2a,2b)$ and has radius $\len$. The inner region defined by the arc contains all $(i,j)$ pairs that are achievable according to Proposition~\ref{prop: len ineq i j}.\ref{prop: len ineq i j: ineq, exist}. As in previous figures, filled circles represent $(i,j)$ pairs that are in $\mss$, and empty circles are those that do not belong to $\mss$. The solid line is \eqref{eq: lower bound, line}. The intersection point $(\isolr, \jsolr)$ is displayed with a square marker.

\begin{figure}
\centering%
\subfigure[$\len = 3.1$: $(\isoli,\jsoli) \in \mss$]{%
\label{fig: ijLS_1p35_detail_in}%
\includegraphics[width=.7\textwidth]{ijLS_1p35_detail_in}%
}\\%\hfill%
\subfigure[$\len = 3.7$: $(\isoli,\jsoli) \notin \mss$]{%
\label{fig: ijLS_1p35_detail_notin}%
\includegraphics[width=.7\textwidth]{ijLS_1p35_detail_notin}%
}%
\caption{Obtaining $(\isoli,\jsoli)$ in Theorem~\ref{theo: funt, form}. Examples with $a=1.35$, $b=1$%
}%
\label{fig: ijLS_1p35_detail}%
\end{figure}%
